Parenting Observational Study E1 Coding

### 2020-03-16 paper/manuscript.Rmd
renamed files and adjusted to calculated rate of JA episodes (per minute)
switched to rate of JA per min

```{r load-exp2-joint-attention-data, echo=F}
load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Science Video","Activity Video"))
d$Age = d$age 
e2ja <- d %>% mutate(bids = bids_tot,
                     age = as.numeric(langcog::scale(age, scale=FALSE)),
                     pja_length = pja_length/1000,
                     cja_length = cja_length/1000,
                     total_lja = total_lja/1000) # convert duration ms -> seconds

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.57,0.92] for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] for total duration of coordinated JA episodes.

@@

modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
summary(modTTR) 
e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.10
p_direction(modTTR, effects="all") # orchestra 73.9%

modMTLD <- stan_glmer(MTLD ~ condition * age + (1|video), data=e1ld)
summary(modMTLD) 
e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -6.27
p_direction(modMTLD, effects="all")

# predict word tokens
tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
summary(tokens_mod)
e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 57.1
p_direction(tokens_mod, effects="all") # orchestra 84.2%

@@

# predict # of conversational turns
modCT <- stan_glmer(Conversational_Turns ~ condition * age + (1|video), data=e1ld)
summary(modCT) 
get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .91
# E1 CT: exp early significant (+ effect)
# E2 CT: age nearly significany (+ effect)
```

@@

### Procedure. 
The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1. 
A second coder independently coded a third of the videos (i.e., 26 of the 84 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.60,0.90] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.59,0.87] for number of passive JA episodes; ICC = 0.78 with 95% CI = [0.58,0.90] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.46,0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] for total duration of coordinated JA episodes.

>>>>

```{r load-exp2-joint-attention-data, echo=F}
load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Science Video","Activity Video"))
d$Age = d$age 
e2ja <- d %>% mutate(bids = bids,
                     age = as.numeric(langcog::scale(age, scale=FALSE)),
                     pja_length = pja_length/1000,
                     cja_length = cja_length/1000,
                     total_lja = total_lja/1000) # convert duration ms -> seconds

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55,0.91] for number of parent bids for JA; ICC = 0.34 with 95% CI = [-0.11,0.67] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11,0.67] for total duration of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24,0.82] for total duration of coordinated JA episodes.

@@

modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
summary(modTTR) 
e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.11
p_direction(modTTR, effects="all") # orchestra 78.7%

modMTLD <- stan_glmer(MTLD ~ condition * age + (1|video), data=e1ld)
summary(modMTLD) 
e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -8.48
p_direction(modMTLD, effects="all")

# predict word tokens
tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
summary(tokens_mod)
e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 59.5
p_direction(tokens_mod, effects="all") # orchestra 89.7%

@@

# predict # of conversational turns
modCT <- stan_glmer(Conversational_Turns ~ condition * age + (1|video), data=e1ld)
summary(modCT) 
get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .92
# E1 CT: exp early significant (+ effect)
# E2 CT: age nearly significany (+ effect)
```

@@

### Procedure. 
The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1. 
To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48,0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61,0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44,0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] for total duration of coordinated JA episodes.

### 2020-03-16 parenting_obs_e1/joint_attention_recoded/parenting_obs_JA_recoded.Rmd
switched to rate of JA per min

```{r echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
library(tidyverse)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(stringr)
library(langcog)
library(xtable)
library(Hmisc)
theme_set(theme_bw())
```

@@

```{r}
combine_datavyu_files <- function(data_dir) {
  d.long <- data.frame()
  files <- dir(data_dir)

@@

  # (assumes something happened early in the vid and late in the vid..)
    vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
    if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))

    jd$phase_length = jd$JointAttention.offset - jd$JointAttention.onset
    if(length(which(jd$phase_length < 0))!=0) print(paste(f, "episode with negative duration!"))
    which(jd$phase_length < 3000) # trim episodes <3 seconds long?

    id <- data.frame(SID = str_replace(f, "_recode.csv", ""), # "012017_01_recode"
                   line = jd$JointAttention.ordinal, # numbered list of episodes e.g. 0 1 2 3 4 5 6 7
                   phase_length = jd$phase_length,
                   pja = jd$JointAttention.pJA, # was episode passive?
                   cja = jd$JointAttention.cJA,
                   bid = jd$JointAttention.bids, # parent bids (1=parent, 0=kid)
                   vid_duration = vid_duration
                )

@@

@@

# summarise per subject
d.raw <- d.long %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
         phase_length = phase_length / 60000) %>%
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute)
d.raw[,2:9] = d.raw[,2:9] / d.raw$vid_duration

@@

@@

# summarise per subject
d.raw_rel <- d.long_rel %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
         phase_length = phase_length / 60000) %>%
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

@@

# Reliability
```{r}
load("Exp1_joint_attention_data_ORIGINAL.RData") # compare Sama to original Exp1 coding
old <- d %>% select(SID, bids, cja, pja, pja_length, cja_length, total_ja, total_lja, bids_tot)

old %>% summarise(bids = mean(bids), cja=mean(cja), pja=mean(pja), l_pja=mean(pja_length), l_cja=mean(cja_length))

d.raw_rel <- d.raw_rel %>%
  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length) %>%
  select(SID, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)

@@

d_rel$pja_diff = (d_rel$pja - d_rel$pja_rel) ^ 2
d_rel$l_pja_diff = (d_rel$l_pja - d_rel$l_pja_rel) ^ 2
d_rel %>% arrange(pja_diff, l_pja_diff)

# compare old vs. d.raw

cor(d.raw$bids, old$bids) # .35
cor(d.raw$cja, old$cja) # .53
cor(d.raw$pja, old$pja) # .34
cor(d.raw$pja_length, old$pja_length) # .32
cor(d.raw$cja_length, old$cja_length) # .52
cor(d.raw$total_ja, old$total_ja) # .27
cor(d.raw$total_lja, old$total_lja) # .31

psych::ICC(cbind(d.raw$pja, old$pja), missing = FALSE, alpha = 0.05)

mean(d_rel$pja - d_rel$pja_rel, na.rm=T)
d_rel$pja - d_rel$pja_rel

@@

bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")])

pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # eps pass JA

cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # eps coord JA

l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # pass JA length

l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # coord JA length

@@

# Compare raters

```{r}
plot(d_rel$pja, d_rel$pja_rel)

plot(d_rel$l_pja, d_rel$l_pja_rel)
```

@@

ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.position="none") 
```

@@

ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total episodes of Joint Attention") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

@@

ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Passive Joint Attention")  +
  langcog::scale_colour_solarized() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

@@

ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()  + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

@@

ggplot(ms_lpja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

@@

ggplot(ms_lcja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

>>>>

```{r include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
library(tidyverse)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(stringr)
library(langcog)
library(xtable)
library(Hmisc)
theme_set(ggthemes::theme_few() + theme(legend.title = element_text(size=18), legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16), axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), axis.title.y = element_text(size=18)))
```

@@

```{r, echo=F}
# for rate coding (JA/minute), we coded the start / end of play sessions because they were not exactly 3 minutes
play_duration <- read.csv("parenting_obs_play_duration_E1.csv", header=T)
play_duration <- play_duration %>% 
  mutate(play_duration = play_stop_sec - play_start_sec)
sort(play_duration$play_duration) # 1 pretty short session: 131 seconds
summary(play_duration$play_duration) # median = 184.5, mean=185.8
# use play_duration$verbalcue_start_sec instead of play_start? (when it exists)

combine_datavyu_files <- function(data_dir) {
  d.long <- data.frame()
  files <- dir(data_dir)

@@

    # (assumes something happened early in the vid and late in the vid..)
    #vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
    #if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))
    SID = str_replace(f, "_recode.csv", "")
    vid_duration = play_duration[which(play_duration$SID==SID),]$play_duration

    jd$phase_length = jd$JointAttention.offset - jd$JointAttention.onset
    if(length(which(jd$phase_length < 0))!=0) print(paste(f, "episode with negative duration!"))

    id <- data.frame(SID = SID, # "012017_01_recode"
                   line = jd$JointAttention.ordinal, # numbered list of episodes e.g. 0 1 2 3 4 5 6 7
                   phase_length = jd$phase_length,
                   pja = jd$JointAttention.pJA, # was episode passive?
                   cja = jd$JointAttention.cJA,
                   bid = jd$JointAttention.bids, # parent bids (1=parent, 0=kid)
                   vid_duration = vid_duration
                )

@@

d.long[which(d.long$phase_length<0),] # 052317_03	7	-93378	0	0	1 (only a bid, so duration doesn't matter)

@@

# summarise per subject
d.raw <- d.long %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60, # seconds to minutes
         phase_length = phase_length / 1000) %>% # ms to seconds
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute and seconds / min duration of JA)
vid_dur = d.raw$vid_duration
d.raw[,2:9] = d.raw[,2:9] / d.raw$vid_duration
d.raw$vid_duration = vid_dur
```

@@

d.long_rel[which(d.long_rel$phase_length<0),] 
# SID=120916_03	 line=7	 -1275	 0	1	 1	 - cja + bid, so should double-check

@@

# summarise per subject
d.raw_rel <- d.long_rel %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60, # seconds to minutes
         phase_length = phase_length / 1000) %>% # ms to seconds
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

@@

# Reliability
```{r}
d.raw_rel <- d.raw_rel %>%
  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length) %>%
  select(SID, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)

@@

@@

bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")]) # .38 [.02, .66]

pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # eps pass JA .06 [-.19, .36]

cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # eps coord JA .59 [.27, .79]

l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # pass JA length .15 [-.13, .46]

l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # coord JA length .37 [-.06, .68]

@@

@@

ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Bids for Joint Attention per Min.") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.position="none") 
```

@@

ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Joint Attention per Min.") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

@@

ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Passive JA per Min.")  +
  langcog::scale_colour_solarized() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

@@

ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Coordinated JA per Min.")  +
  langcog::scale_colour_solarized()  + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

@@

ggplot(ms_lpja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Seconds of Passive JA per Min.")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

@@

ggplot(ms_lcja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Seconds of Coordinated JA per Min.")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```
